---
title: "Week 9 Practice"
author: "Alan Kessler"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

A lot of the problems this week are related so for chapter 12, I will base multiple problems on the data in problem 12.6. Then I will complete a few of the problems

The following packages are used this week:

```{r libraries, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
```

# Chapter 12

## Data

The data used in the next two problems is from Chapter 12: Simple Regression Analysis and Correlation, Section 12.3: Determining the Equation of the Regression Line, problem 12.6 [(Black, 2016, p. 435)](#ref).

The data originally from the problem is manually entered into vectors to create a data frame.

```{r data1}
x <- c(12, 21, 28, 8, 20)
y <- c(17, 15, 22, 19, 24)
df <- data.frame(x, y)

kable(df, format="html") %>%
  kable_styling(full_width = FALSE) 
```

## Problem 1

This problem is from Chapter 12: Simple Regression Analysis and Correlation, Section 12.6: Coefficient of Determination [(Black, 2016, p. 448)](#ref).

>12.32 Compute $r^2$ for Problem 12.24 (Problem 12.6). Discuss the value of $r^2$ obtained.

```{r p1}
m <- summary(lm(y ~ x))
round(m$r.squared, 4)
```

The value calculated above shows that x explains about 12% of the variability of $y$. Like the section discusses, the acceptability of this result depends on the context of the use of the model.

## Problem 2 

This problem is from Chapter 12: Simple Regression Analysis and Correlation, Section 12.7: Hypothesis Tests for the Slope of the Regression Model and Testing the Overall Model [(Black, 2016, p. 453)](#ref).

>12.38 Test the slope of the regression line determined in Problem 12.6. Use $\alpha=0.05$. 

```{r p2}
m$coefficients[2,]
```

The result is that x is not a signficant variable in the model at the specified confidence level.

# Chapter 13

This problem is from Chapter 13: Multiple Regression Analysis, Section 13.1: The Multiple Regression Model [(Black, 2016, p. 480)](#ref).

>13.2 Use a computer to develop the equation of the regression model for the following data. Comment on the regression coefficientss. Determine the predicted value of y for $x_1 = 33$, $x_2 = 29$, and $x_3 = 13$. 

## Data

```{r data2}
y <- c(114, 94, 87, 98, 101)
x1 <- c(21, 43, 56, 19, 29)
x2 <- c(6, 25, 42, 27, 20)
x3 <- c(5, 8, 25, 9, 12)
df <- data.frame(y, x1, x2, x3)

kable(df, format="html") %>%
  kable_styling(full_width = FALSE) 
```

```{r p3}
m <- lm(y ~ x1 + x2 + x3, data = df)
summary(m)
```

Based on the results, with this small of a sample size, the model and variables are not statistically significant. The $r^2$ shows that the model explains almost all of the variance in $y$. Variables $x_1$ and $x_2$ have a negative relationship with $y$ while $x_3$ has a postive relationship. 

```{r p4}
new <- data.frame(x1 = 33, x2 = 29, x3 = 13)
predict(m, newdata = new)
```

The above code calculates the preditced value for the inputs shown in the problem. 

# References {#ref}

Black, K. (2016). *Business statistics : for contemporary decision making*. Hoboken: Wiley.


