---
title: "Week 6 Practice"
author: "Alan Kessler"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

A lot of the problems this week can be done very quickly in R so I am submitting two problems for practice this week. 

The following packages are used this week:

```{r libraries, message=FALSE, warning=FALSE}
library(dplyr)
library(knitr)
library(kableExtra)
```

# Problem 1 

This problem is from Chapter 16: Analysis of Categorical Data, Section 16.1: Chi-Square Goodness-of-Fit Test [(Black, 2016, p. 608)](#ref).

>16.8 The Springfield Emergency Medical Service keeps records of emergency telephone calls. A study of 150 five-minute time intervals resulted in the distribution of number of calls that follows. For example, during 18 of the 5-minute intervals, no calls occured. Use the chi-square goodness-of-fit test and $\alpha = 0.01$ to determine whether this distribution is Poisson.

## The Data

The data originally from the problem is manually entered into vectors to create a data frame.

```{r data1}
Frequency <- c(18, 28, 47, 21, 16, 11, 9)
df <- data.frame(Frequency)
rownames(df) <- c("0", "1", "2", "3", "4", "5", "6 or more")

kable(df, format="html") %>%
  kable_styling(full_width = FALSE) %>%
  group_rows("Calls", 1, 7)
```

## Test for Goodness-of-Fit

```{r test1}
# Fill in Poisson probabilities
df$ncalls <- (0:6)
lambda <- sum(df$ncalls * df$Frequency) / sum(df$Frequency)
df$PoisProbs <- dpois(df$ncalls, lambda) 

# Replace the last cell to reflect the inequality
df$PoisProbs[7] <- 1 - sum(df$PoisProbs[0:6])

chisq.test(x = df$Frequency, p = df$PoisProbs)
```

The p-value is greater than 0.01 which suggest that we cannot reject the null hypothesis that the number of calls is Poisson distributed at this value for $\alpha$. 

# Problem 2 

This problem is from Chapter 16: Analysis of Categorical Data, Section 16.2: Contingency Analysis: Chi-Square Test of Independence [(Black, 2016, p. 614)](#ref).

>16.12 Use the following contingency table and chi-square test of independence to determine whether social class is independent of number of children in a family. Let $\alpha = 0.05$.

## The Data

The data originally from the problem is manually entered into a table.

```{r data}
ClassStudy <- as.table(rbind(c(7, 18, 6), 
                             c(9, 38, 23), 
                             c(34, 97, 58), 
                             c(47, 31, 30)))

# Label columns and rows
dimnames(ClassStudy) <- list(NumberChildren = c("0", "1", "2 or 3", "More than 3"),
                             SocialClass = c("Lower","Middle", "Upper"))


kable(ClassStudy, format="html") %>%
  kable_styling(full_width = FALSE) %>%
  add_header_above(c(" ", "Social Class" = 3)) %>%
  group_rows("Children", 1, 4)
```

## Test for Independence 

```{r test}
chisq.test(ClassStudy)
```

The p-value is less than 0.05 which suggests that we can reject the null hypothesis that social class is independent of the number of children in a family at this value for $\alpha$. 

# References {#ref}

Black, K. (2016). *Business statistics : for contemporary decision making*. Hoboken: Wiley.


